\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/experiment.tex
revision of PBS description
[experiment] table

\textbf{Setup.}
%\fengwei{I would suggest to add references for devices such as
%Pi, ATMEGA32U4 board, Yamazawa, etc.}
As mentioned in Section~\ref{sec:badusb},
our \tool only requires common components that are easily accessible online or
in any electronic store. Here we choose the following parts to build a
prototype. To begin with, we choose the Raspberry Pi 4B~\cite{pi4b} as the embedded Single Board
Computer inside \tool, which is powerful enough to process video data and has
an onboard WiFi chip. As for the HID Emulator, we use an Atmel ATMEGA32U4 board~\cite{atmel}
with USB protocol support, which is able to emulate multiple HID devices
with our modified firmware. About the USB 3.x Hub, we use one from the
UGREEN~\cite{ugreen}, which supports HDMI, USB 2.0, and many other exported peripherals.
Apart from these essential parts, we also use an auxiliary power-bank to
provide power for the Raspberry Pi and the mobile devices used by the victim.
The image of our \tool prototype can be found in Figure~\ref{fig:armory}.
\mycircled{A} is a Huawei mobile phone as the victim's device; \mycircled{B} is a compact look of \tool prototype; \mycircled{1} is the USB 3.x Hub; \mycircled{2} is a Raspberry Pi 4B as the Single Board Computer; \mycircled{3} is an auxiliary power bank; \mycircled{4} is the Video Capture Card; \mycircled{5} is an Atmel ATMEGA32U4 board as the HID Emulator.
%\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
%2, 3, 4, and 5?}\hongyi{Is the caption sufficient? If explain here, I feel quite redundant}
%\fengwei{I think it is necessary to explain them in the text again.}

@@

%\fengwei{do we need a reference for OCR?}
%\hongyi{we have discussed this and decide no need.}
\subsection{Video Capture Mode}

During the experiment of privacy extraction via our video capture mode, we chose \textit{HUAWEI P30}, a
smartphone in EMUI 9.1 (Android 9.0 based) with a USB Type-C interface, as the
target device.  In the privacy extraction experiment, \tool passively captured video
from the victim's device and used \textit{OpenCV} to identify the sensitive
information from the video stream.  When the victim viewed text or photos with
text, \tool used the techniques of Optical Character Recognition (OCR)  to
extract text from corresponding video frames. In this experiment, the attacker had
successfully extracted text like name, address, ID number, and other sensitive
personal information. We also tested the payment code extractor, which enables
an attacker to identify payment code in the video stream and perform transactions
without the password. As this is also a part of our case study, more details about
the extracted sensitive data can be found in Section~\ref{subsec:case_study} and
Table~\ref{table:information_extracted}.

@@

\begin{table*}[t]
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		\textbf{Keyword}  & \textbf{Text}                                                                                                                          & \textbf{Name}                           & \textbf{Frame Number} \\ \hline
		username & X 8B cas.******.edu.cn Username: 11****18 Password:                                                                           & \textless{}user1\textgreater{} & 385          \\ \hline
		username & Login Weibo Login with SMS and verification code ...... +86 151****4587 & \textless{}user5\textgreater{} & 1947         \\ \hline
		username & QQ 14*****50| Login with phone number New user registration 2345678 9 0                                                       & \textless{}user3\textgreater{} & 4308         \\ \hline
		username & connect to *** username h*****l Save account information Open VPN.....                                                        & \textless{}user6\textgreater{} & 7925         \\ \hline
		+86      & Login with phone number ...... +86 186****2483 |                                                                              & \textless{}user1\textgreater{} & 313          \\ \hline
	\end{tabular}
	\linebreak
	\caption{Examples of Searching OCR Results with Keywords.}
	\label{tab:ocr_keyword_example}
\end{table*}

>>>>

\textbf{Setup.}
%\fengwei{I would suggest to add references for devices such as
%Pi, ATMEGA32U4 board, Yamazawa, etc.}
As mentioned in Section~\ref{sec:badusb},
our \tool only requires common components that are easily accessible online or
in any electronic store. Here we choose the following parts to build a
prototype. To begin with, we choose the Raspberry Pi 4B~\cite{pi4b} as the embedded Single Board
Computer inside \tool, which is powerful enough to process video data and has
an onboard WiFi chip. As for the HID Emulator, we use an Atmel ATMEGA32U4 board~\cite{atmel}
with USB protocol support, which is able to emulate multiple HID devices
with our modified firmware. About the USB 3.x Hub, we use one from the
UGREEN~\cite{ugreen}, which supports HDMI, USB 2.0, and many other exported peripherals.
Apart from these essential parts, we also use an auxiliary power-bank to
provide power for the Raspberry Pi and the mobile devices used by the victim.
The image of our \tool prototype can be found in Figure~\ref{fig:armory}.
\mycircled{A} is a Huawei mobile phone as the victim's device; \mycircled{B} is a compact look of \tool prototype; \mycircled{1} is the USB 3.x Hub; \mycircled{2} is a Raspberry Pi 4B as the Single Board Computer; \mycircled{3} is an auxiliary power bank; \mycircled{4} is the Video Capture Card; \mycircled{5} is an Atmel ATMEGA32U4 board as the HID Emulator.
%\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
%2, 3, 4, and 5?}\hongyi{Is the caption sufficient? If explain here, I feel quite redundant}
\fengwei{I think it is necessary to explain them in the text again.}

@@

\subsection{Video Capture Mode}

During the experiment of privacy extraction via our video capture mode, we chose \textit{HUAWEI P30}, a
smartphone in EMUI 9.1 (Android 9.0 based) with a USB Type-C interface, as the
target device.  In the privacy extraction experiment, \tool passively captured video
from the victim's device and used \textit{OpenCV} to identify the sensitive
information from the video stream.  When the victim viewed text or photos with
text, \tool used the techniques of Optical Character Recognition (OCR) \fengwei{do we need a reference for OCR?} to
extract text from corresponding video frames. In this experiment, the attacker had
successfully extracted text like name, address, ID number, and other sensitive
personal information. We also tested the payment code extractor, which enables
an attacker to identify payment code in the video stream and perform transactions
without the password. As this is also a part of our case study, more details about
the extracted sensitive data can be found in Section~\ref{subsec:case_study} and
Table~\ref{table:information_extracted}.

@@

\begin{table*}[t]
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		\textbf{Keyword} & \textbf{Text}                                                             & \textbf{Name}                                   & \textbackslash{}textbf\{Frame Number\} \\ \hline
		username                          & X 8B cas.******.edu.cn Username: 11****18 Password:                                        & \textless{}user1\textgreater{} & 385                                    \\ \hline
		username                          & Login Weibo Login with SMS and verification code ...... +86 151****4587                    & \textless{}user5\textgreater{} & 1947                                   \\ \hline
		username                          & QQ 14*****50| Login with phone number New user registration 2345678 9 0                    & \textless{}user3\textgreater{} & 4308                                   \\ \hline
		username                          & connect to *** username h*****l Save account information Open VPN.....                     & \textless{}user6\textgreater{} & 7925                                   \\ \hline
		phone number                      & Login with phone number ...... +86 186****2483 |                                           & \textless{}user1\textgreater{} & 313                                    \\ \hline
		phone number                      & Log in with your mobile phone number. ...... mobile phone number 131****9310 & \textless{}user9\textgreater{} & 210                                    \\ \hline
		@                                 & contact email 30*******7G@qq.com, contact phone 027-88******                               & \textless{}user7\textgreater{} & 5324                                   \\ \hline
		@                                 & Account 73*****5@qq.com @qq.com @163.com @gmail.com 	......      & \textless{}user6\textgreater{} & 621                                    \\ \hline
	\end{tabular}
	\linebreak
	\caption{Examples of Searching OCR Results with Keywords.}
	\label{tab:ocr_keyword_example}
\end{table*}
